%$Header: /cvsroot/latex-beamer/latex-beamer/solutions/generic-talks/generic-ornate-15min-45min.en.tex,v 1.4 2004/10/07 20:53:08 tantau Exp $
\documentclass{beamer}
\mode<presentation>
{
  \usecolortheme{seahorse}
  \usefonttheme{professionalfonts}
  \useinnertheme{rounded}
  \useoutertheme{shadow}
%  \useoutertheme{smoothbars}
}
%\setbeamertemplate{background canvas}[vertical shading][bottom=white!10,top=blue!5]
\usepackage{verbatim} 
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{pgf,pgfarrows,pgfnodes,pgfautomata,pgfheaps,pgfshade}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{graphics}
\usepackage{graphicx}
%\usepackage{psfig}
\usepackage{algorithmic}

\title
{Open source CAD tool for electronic and electrical engineers}

\author[]
{Yogesh Dilip Save}
\institute
{
  Indian Institute of Technology, Bombay
}
%\pgfdeclareimage[height=0.7cm]{university-logo}{iitblogo.eps}
%\logo{\pgfuseimage{university-logo}}


\date[seminar] % (optional)
{\today}


\begin{document}
%***************************************************************************************
\begin{frame}
  \titlepage
\end{frame}
%***************************************************************************************
\begin{frame}
  \frametitle{Presentation Outline}
  \tableofcontents
\end{frame}
%***************************************************************************************

\section{Modules}
\begin{frame}
 \frametitle{Modules}
\begin{block}{}
\begin{itemize}
\item eeschema -- Schematic Editor
\item CvPCB -- Component-Footprint mapper
\item pcbnew -- PCB Layout Editor
\item Analysis Inserter
\item Component Model Builder
\item Component Sub-circuit Builder
\item Kicad to Ngspice netlist converter
\item Circuit Simulator -- Ngspice
\item Scilab based circuit simulator -- SMCSim
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\frametitle{eeschema}
\begin{block}{Problems}
\begin{itemize}
\item No fictitious components (sources) 
\item[Sol:] Build a library of different kind of voltage and current sources (pulse, sine, exponential etc.)
\item Too many components
\item[Sol:] Build own libraries (include the components supported by ngspice (explicitly or implicitly)). \\
   Libraries (analogSpice (analog components) and digitalSpice (digital components)) can be built by
   \begin{enumerate}
     \item Creating own components.
     \item Coping components from existing libraries.
   \end{enumerate}
\item No measurement modules
\item[Sol:] Build a library which gives you functionality of printing and plotting solution.  
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\begin{block}{ CvPCB and pcbnew}
Add footprint for new components.
\end{block}
\end{frame}

\begin{frame}
\begin{block}{Netlist Converter}
\begin{itemize}
\item Insert parameters for fictitious components
\item Convert IC into discrete blocks
\item Insert D-A and A-D converter at appropriate place,
\item Insert plotting and printing statement in netlist.
\item Find current through all components.  
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\begin{block}{Analysis Inserter}
\begin{itemize}
\item Insert type of analysis
\item Option of analysis
\item Option of simulator
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
  \begin{block}{Model Editor}
    \begin{itemize}
            \item Provides facility to define new model.
    \begin{itemize}
            \item Diode
            \item Bipolar Junction Transistor (BJT)
            \item Metal Oxide Semiconductor (MOS)
            \item Junction Field Effect Transistor (JFET)
            \item IGBT
            \item Magnetic core
    \end{itemize}
            \item Provides facility to edit existing model.
            \item Provides help related to model parameter.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \begin{block}{Sub-circuit Editor}
    \begin{itemize}
            \item Provides facility to define new components.
    \begin{itemize}
            \item Op-amp
            \item Timer-IC555
    \end{itemize}
            \item Provides facility to edit existing sub-circuit.
            \item Provides help related to components parameters.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
\begin{block}{Circuit Simulator}
\begin{itemize}
\item Ngspice
\item SMCSim
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\begin{block}{Future Plan}
\begin{itemize}
\item More consolidation of Kicad NgSpice netlist converter (nearly 10 days).
\item Build a descent GUI and remove the bugs in integration (nearly 10 days).
\item Simulate more examples which cover most of the syllabus of undergraduate in circuit theory (nearly 10 days). 
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\begin{block}{May be...........}
\begin{itemize}
\item Scilab based simulator 
\item Extend Scilab based simulator for mix circuit simulation
\end{itemize}
\end{block}
\end{frame}

\end{document}

